Hydra Battles and Cie

### 2021-08-27 doc/part-hydras.tex
re-reading chapter 2 (partially)

Let us look at the second sub-goal of the induction.

@@

\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Examples.html}{Hydra.Hydra\_Examples}}

\input{movies/snippets/Hydra_Examples/heightLtSizea}

The first subgoal is easily solvable, using some arithmetic. We let the reader look at the source. The second and third are
almost trivial.

@@

\input{movies/snippets/Hydra_Definitions/S0Def}

\input{movies/snippets/Hydra_Definitions/R1Def}

@@

%% TODO display sub-goals when fixed

@@

But this style leads to clumsy statements, and generates too many sub-goals in interactive proofs (although often solved with \texttt{auto} or \texttt{eauto}).

@@

On the other hand, the following attempt fails, because of the unprovable first sub-goal (please notice that the second sub-goal is easy to solve !).

>>>>

Let us look at the second subgoal of the induction.

@@

\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Examples.html}{Hydra.Hydra\_Examples}}
\input{movies/snippets/Hydra_Examples/heightLtSizea}

The first subgoal is easily solvable, using some arithmetic.
The second and third ones are
almost trivial. We let the reader look at the source. 
\input{movies/snippets/Hydra_Examples/heightLtSizez}

@@

\input{movies/snippets/Hydra_Definitions/S0Def}
\input{movies/snippets/Hydra_Definitions/R1Def}

@@

%% TODO display subgoals when fixed

@@

But this style leads to clumsy statements, and generates too many subgoals in interactive proofs (although often solved with \texttt{auto} or \texttt{eauto}).

@@

On the other hand, the following attempt fails, because of the unprovable first subgoal (please notice that the second subgoal is easy to solve !).
